---
title: stats
author: "Yadu"
date: "July 25, 2015"
output: html_document
---
First, we need to load the required packages, which are ggplot2 and datasets:
```{r}
library(ggplot2)
library(datasets)
```

Next, we do frequency histograms for four of the numerical quantities which are mean ozone, solar radiation, average wind speed, and maximum daily temperature:
```{r qplot, fig.width=4, fig.height=3}
#This histogram is skewed to the right.
qplot(Ozone, ylab = "number of observations", data = airquality, binwidth = 10) 
#This histogram is skewed to the left. 
qplot(Solar.R, ylab = "number of observations", data = airquality, binwidth = 10)
#There are more observations that have a lower wind speed.
qplot(Wind, ylab = "number of observations", data = airquality, binwidth = 10)
#This histogram is skewed to the left. 
qplot(Temp, ylab = "number of observations", data = airquality,
      binwidth = 10)

```

Next, we obtain the box and whisker plots for solar radiation and maximum daily temperature:
```{r boxplot, fig.width=4, fig.height=3}
#The mean is at 185.9 Langleys.
boxplot(airquality$`Solar.R`)
#The mean is at 77.88 degrees F
boxplot(airquality$`Temp`)
```

The summary for the data is as follows:
```{r}
summary(airquality)
```

We also obtain the linear correlation coefficient between temperature and solar radiation as well as between average wind speed and maximum daily temperature: 
```{r}
#There is absolutely no correlation. 
cor(airquality$`Temp`, airquality$`Solar.R`)

#There is absolutely no correlation.
cor(airquality$`Wind`, airquality$`Ozone`)
```

Finally, we obtain a scatterplot for solar radiation and maximum temperature with a line of best fit:
```{r ggplot, fig.width=4, fig.height=3}
ggplot(data = airquality, aes(x = Solar.R, y = Temp)) + 
geom_point(shape = 1) + 
geom_smooth(method = lm)
```

Scatterplot for mean ozone and average windspeed with a line of best fit:
```{r}
ggplot(data = airquality, aes(x = Ozone, y = Wind)) + 
geom_point(shape = 1) + 
geom_smooth(method = lm)
```

Scatterplot for solar radiation and maximum temperature with a Loess curve of best fit: 
```{r}
ggplot(data = airquality, aes(x = Solar.R, y = Temp)) + 
geom_point(shape = 1) + 
geom_smooth()
```

Scatterplot for mean ozone and average windspeed with a Loess curve of best fit:
```{r}
ggplot(data = airquality, aes(x = Ozone, y = Wind)) + 
geom_point(shape = 1) + 
geom_smooth()


#http://rpubs.com/catlin/DPBWeek6
#http://www.cookbook-r.com/Graphs/Scatterplots_(ggplot2)/

```


